IALE 2015 Analysis

### 2015-07-03 iale2015_sem.Rmd
added titles to the calls to the pairs plotting functions for the oak and bay laurel data frames

Make a pairs plot of the continuous variables for UMCA plots.
```{r pairs plot}
# Helper functions for `pairs`
panel.hist <- function(x, ...)
{
      usr <- par("usr"); on.exit(par(usr))
      par(usr = c(usr[1:2], 0, 1.5) )
      h <- hist(x, plot = FALSE)
      breaks <- h$breaks; nB <- length(breaks)
      y <- h$counts; y <- y/max(y)
      rect(breaks[-nB], 0, breaks[-1], y, col = "cyan", ...)
}
panel.cor <- function(x, y, digits = 2, prefix = "", cex.cor, ...)
{
      usr <- par("usr"); on.exit(par(usr))
      par(usr = c(0, 1, 0, 1))
      r <- abs(cor(x, y, use = "na.or.complete"))
      txt <- format(c(r, 0.123456789), digits = digits)[1]
      txt <- paste0(prefix, txt)
      if(missing(cex.cor)) cex.cor <- 0.8/strwidth(txt)
      text(0.5, 0.5, txt, cex = cex.cor * r)
}

@@

pairs(select(plots_umca, -plotid, -year, -starts_with("psi"), -tagged_rich, -untagged_rich), lower.panel = panel.cor, diag.panel = panel.hist)
```

@@

```{r oak_sod pairs plot}
class(oak_sod)
oak_sod <- ungroup(oak_sod)

pairs(select(oak_sod, -plotid, -year, -starts_with("psi"), -tagged_rich, -untagged_rich), lower.panel = panel.cor, diag.panel = panel.hist)
```

>>>>

Make a pairs plot of the continuous variables for UMCA plots.
```{r umca sod pairs plot}
# Helper functions for `pairs`
panel.hist <- function(x, ...)
{
      usr <- par("usr"); on.exit(par(usr))
      par(usr = c(usr[1:2], 0, 1.5) )
      h <- hist(x, plot = FALSE)
      breaks <- h$breaks; nB <- length(breaks)
      y <- h$counts; y <- y/max(y)
      rect(breaks[-nB], 0, breaks[-1], y, col = "cyan", ...)
}
panel.cor <- function(x, y, digits = 2, prefix = "", cex.cor, ...)
{
      usr <- par("usr"); on.exit(par(usr))
      par(usr = c(0, 1, 0, 1))
      r <- abs(cor(x, y, use = "na.or.complete"))
      txt <- format(c(r, 0.123456789), digits = digits)[1]
      txt <- paste0(prefix, txt)
      if(missing(cex.cor)) cex.cor <- 0.8/strwidth(txt)
      text(0.5, 0.5, txt, cex = cex.cor * r)
}

@@

pairs(select(plots_umca, -plotid, -year, -starts_with("psi"), -tagged_rich, -untagged_rich), lower.panel = panel.cor, diag.panel = panel.hist, main = "UMCA SOD Data")
```

@@

```{r oak_sod pairs plot}
class(oak_sod)
oak_sod <- ungroup(oak_sod)
pairs(select(oak_sod, -plotid, -year, -starts_with("psi"), -tagged_rich, -untagged_rich), lower.panel = panel.cor, diag.panel = panel.hist, main = "Oak_SOD Data")
```
